%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[11pt]{resume} % Use the resume class

% \usepackage{ebgaramond} % Use the EB Garamond font
\usepackage{mathptmx}
\usepackage{fontawesome}
\usepackage[colorlinks=true, urlcolor=black, linkcolor=black, citecolor=black, pdfborder={0 0 0}, pdfhighlight=/N]{hyperref}
\usepackage{enumitem}
%----------------------------------------------------------------------------------------
% PERSONAL INFO
%----------------------------------------------------------------------------------------
\name{Pei-Chi Chen}

\address{\faEnvelope\ b1989413@gmail.com $\,|\,$ \faGithub\ \href{https://github.com/PeiChiChen}{PeiChiChen}}
% \address{\faGithub\ \href{https://github.com/PeiChiChen}{github.com/PeiChiChen}}

%----------------------------------------------------------------------------------------
\begin{document}
\vspace{-5pt}
%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{\Large Education}

\begin{rSubsection}{\large\textbf{M.S.}, National Yang Ming Chiao Tung University}{\textit{Sep. 2022 -- Aug. 2024}}{\href{https://aigp.ece.nycu.edu.tw/}{Graduate Degree program of Artificial Intelligence}}{Hsinchu, Taiwan}
\item Thesis: Enhancing Coherence and Fidelity in Camouflaged Image Generation
\item Advised by 
\href{https://basiclab.lab.nycu.edu.tw/}{Prof. Hong-Han Shuai} and \href{https://www.csie.ntu.edu.tw/~wenhuang/}{Prof. Wen-Huang Cheng}
\item Selected courses: \textit{Applied Computer Vision, Cloud Computing and Big Data Analysis, Optimization Theory and Application, Information Theory}
\end{rSubsection}
\begin{rSubsection}{\large\textbf{B.S.}, National Tsing Hua University}{\textit{Sep. 2018 -- Jun. 2022}}{\href{https://ess.site.nthu.edu.tw/}{Engineering and System Science}}{Hsinchu, Taiwan}
\item GPA: 4.17 / 4.3 (Ranked 1 / 90 )
\item Selected courses: \textit{Numerical Analysis, Introduction to Machine Learning, Introduction to Image Processing, Probability and Statistics, Introduction to Artificial Intelligence, Queuing Theory, Computer Architecture} 
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{\Large Experience}

\begin{rSubsection}{\href{https://www.iis.sinica.edu.tw/zh/index.html}{\large Institute of Information Science, Academia Sinica}}{\textit{Oct. 2024 -- Present}}{Research Assistant}{Taipei, Taiwan}
  \item Action selection in Diffusion Policy for robotic manipulation tasks
  \item Advised by \href{https://homepage.iis.sinica.edu.tw/~liutyng/}{Dr. Tyng-Luh Liu}
  \item Co-advised by \href{https://htchen.github.io/}{Prof. Hwann-Tzong Chen} in NTHU and \href{https://twke18.github.io/}{Prof. Tsung-Wei Ke} in NTU
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS
%----------------------------------------------------------------------------------------
\begin{rSection}{\Large Publications}
\begin{enumerate}[leftmargin=2pt, label={[\arabic*]}]
    \item \textbf{Pei-Chi Chen}, Yi Yao, Chan-Feng Hsu, Hongxia Xie, Hung-Jen Chen, Hong-Han Shuai, Wen-Huang Cheng. \textbf{Foreground Focus: Enhancing Coherence and Fidelity in Camouflaged Image Generation.} ICME \textbf{\color{red}{(oral)}}, 2025. \href{https://arxiv.org/abs/2504.02180}{\color{blue}{paper}}
    \item Li-Wu Tsao, Hao-Tang Tsui, Yu-Rou Tuan, \textbf{Pei-Chi Chen}, Kuan-Lin Wang, Jhih-Ciang Wu, Hong-Han Shuai, Wen-Huang Cheng. \textbf{TrajPrompt: Aligning Color Trajectory with Vision-Language Representations.} ECCV 2024. \href{https://link.springer.com/chapter/10.1007/978-3-031-72940-9_16}{\color{blue}{paper}}
    \item Dinesh Bhalothia, Wei-Hao Hsiung, Shou-Shiun Yang, Che Yan, \textbf{Pei-Chi Chen}, et al. \textbf{Submillisecond Laser Annealing Induced Surface and Subsurface Restructuring of Cu–Ni–Pd Trimetallic Nanocatalyst Promotes Thermal CO2 Reduction.} ACS Appl. Energy Mater. 2021. \href{https://pubs.acs.org/doi/10.1021/acsaem.1c02823}{\color{blue}{paper}}

\end{enumerate}
\end{rSection}

%----------------------------------------------------------------------------------------
% AWARDS
%----------------------------------------------------------------------------------------
\begin{rSection}{\Large Honors and Scholarships}
\begin{tabular}{@{}p{2cm}@{\hspace{0.5cm}}p{13cm}@{}}
2023 & Foxconn Technology \& NYCU Scholarship\\
2022 & Foxconn Technology \& NYCU Scholarship \\
2022         & GARMIN Scholarship \\
2022         & FamilyMart AI Scholarship \\
2022         & Phi Tau Phi Scholastic Honor Society – Honorary Membership \\
2020         & Dr. Shun-Yi Chu Zyxel Scholarship \\
2018$\sim$2022 & Outstanding Academic Achievement Award (6 of 8 semesters)
\end{tabular}
\end{rSection}

\begin{rSection}{\Large Professional Services}
\begin{tabular}{@{}p{2cm}@{\hspace{0.5cm}}p{13cm}@{}}
2026 & \textbf{Reviewer}, Neural Networks (NEUNET)
\\
2026 & \textbf{Reviewer}, IEEE International Conference on Multimedia \& Expo (ICME)
\\
2025 & \textbf{Reviewer}, IEEE International Conference on Advanced Video and Signal-Based Surveillance (AVSS)
\\
2025 & \textbf{Reviewer}, IEEE International Conference on Multimedia \& Expo (ICME)
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS & RESEARCH
%----------------------------------------------------------------------------------------
\begin{rSection}{\Large Projects}

\begin{rSubsection}{\textbf{Traffic Light Detection and Recognition (in collaboration with GARMIN)}}{\textit{Sep. 2022 -- Jun. 2023}}{}{}
\item Developing a system for detecting traffic lights and countdown timers under various weather conditions. 
\item Addressing the data scarcity issue in vertical traffic light countdown detection and recognition, \textbf{improving accuracy from 24.3\% to 75.7\%}
\end{rSubsection}

\begin{rSubsection}{\textbf{Histone Image Reconstruction}}{\textit{Sep. 2021 -- Jan. 2022}}{}{}
\item Reconstructing H2B histone fluorescence images from COBRI inputs using U-Net architecture.
\end{rSubsection}
\begin{rSubsection}{\textbf{Lung Tumor Segmentation}}{\textit{Spring, 2021}}{}{}
\item Employing a dual-branch CNN to segment tumor regions from fluorescence microscopy images.
\item \textbf{Reaching an accuracy of 91.3$\%$.}
\end{rSubsection}

\begin{rSubsection}{\textbf{Analysis of Atomic Lattices}}{\textit{Spring, 2021}}{}{}
\item Analyzing lattice structures in material high-resolution TEM images using image processing techniques to identify atom types.
\vspace{3pt}
\item The project was accepted by ACS Appl. Energy Mater. (please refer to Publications)
\end{rSubsection}
\end{rSection}

\begin{rSection}{\Large Invited Talks}
\begin{tabular}{@{}p{2cm}@{\hspace{0.5cm}}p{13cm}@{}}
2025 & \href{https://www.youtube.com/watch?v=eO6DV7CIbKs}{A Step-by-Step Guide to Paper Reading and Presentation}, invited by Prof. HongXia Xie, Jilin University, China
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
\end{document}
